LCA in R

### 2022-08-31 example_analysis/Daniel_LCA.Rmd
Updates 23 August
Updated the manuscript.

All the references are now in the [@key] format.  New .bib file  with references has been made.

Reworked the model fit section to reflect statistics tidySEM reports.
Stated that LRT cannot be used.
Referred to the bootstrapped LRT being available albeit extremely slow; we are currently developing a faster version.

Adjusted classification diagnostics to reflect what tidySEM provides. Entropy is finished. Needs more information on the range of the posterior classification probabilities by most likely class membership and the range of the sample size.

@@

# Part 1: Using mclust [incomplete]

```{r}
library(mclust)
```

```{r}
# Fit 1-9 class model
model <- Mclust(data)
```

>>>>

USING TIDYSEM:

see functions starting in mx

```{r}
library(tidySEM)
df <- data_mix_ordinal
df[1:4] <- lapply(df, ordered)
mx_lca(data = df,
       classes = 2) -> res
```

```{r}
res$class1
res$latentVars
```

USING DIFFERENT PACKAGES

@@

```{r}
#adjust this code
# The argument `classes` indicates which class solutions should be estimated (e.g., 1 through 6).
# The argument `variances` specifies whether variances should be `"equal"` or `"varying"` across classes.
# The argument `covariances` specifies whether covariances should be constrained to `"zero"`, `"equal"` or `"varying"` across classes.
tidySEM::mx_profiles(classes, variances, covariances)
```

After all models have been estimated, the function `tidySEM::table_fit()` can be used to obtain a model fit table suitable for determining the optimal model according to best practices.
Note however that this table does not include the bootstrapped likelihood ratio test (BLRT) by default,
because this test is very computationally expensive.
It is recommended to use the function `tidySEM::BLRT()` to compare a shortlist of likely candidate models based on other fit indices.
